Self Regulation Ontology Retest Data Report

### 2018-01-17 code/SRO_Report.Rmd
updates

```{r echo=FALSE}
#Get variables of interest from Ian's release
tmp1 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_11-22-2017/meaningful_variables.csv')
tmp2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_11-22-2017/meaningful_variables_noDDM.csv')
tmp3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_11-22-2017/meaningful_variables_EZ.csv')
retest_report_vars = c(names(tmp1), names(tmp2), names(tmp3))
retest_report_vars = unique(retest_report_vars)
lit_rev_vars = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% retest_report_vars == FALSE)])
retest_report_vars = c(retest_report_vars, lit_rev_vars)
rm(tmp1, tmp2, tmp3, lit_rev_vars)
```

### Load time 1 data
```{r}
test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/t1_data/variables_exhaustive.csv')

@@

```{r}
test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/t1_data/variables_exhaustive.csv')

@@

### Load time 2 data 
```{r}
retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/variables_exhaustive.csv')

@@

```{r}
hddm_refits <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/hddm_refits_exhaustive.csv')

@@

@@

ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE)
```

@@

```{r message=FALSE, warning=FALSE}
boot_df <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/bootstrap_merged.csv')

@@

ggsave('Bootstrap_Poster_Plot_t.jpg', plot = p6_t, device = "jpeg", path = "../output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE)
```

@@

ggsave('Variance_Breakdown_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 24, height = 20, units = "in")
rm(tmp, labels)
```

@@

```{r}
aggregate(value ~task+key, FUN=mean, data=tmp)

tmp%>%
  group_by(task, key) %>%
  summarise(median = median(value),
            sd = sd(value))
```

Summarizing for clearer presentation. This grap is currently using the bootstrapped reliabilities and is therefore messier than if just using the point estimates.

@@

ggsave('Variance_Breakdown_Plot_Summary.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in")
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            min_icc = min(icc),
            max_icc = max(icc),
            min_spearman = min(spearman),
            max_spearman = max(spearman),
            num_measures = n(),
            num_trials = unique(num_all_trials))%>%
  arrange(-median_icc, -median_spearman)

@@

>>>>

```{r echo=FALSE}
#Get variables of interest from Ian's release
tmp1 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-15-2018/meaningful_variables.csv')
tmp2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-15-2018/meaningful_variables_noDDM.csv')
tmp3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-15-2018/meaningful_variables_EZ.csv')
retest_report_vars = c(names(tmp1), names(tmp2), names(tmp3))
retest_report_vars = unique(retest_report_vars)
lit_rev_vars = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% retest_report_vars == FALSE)])
retest_report_vars = c(retest_report_vars, lit_rev_vars)
rm(tmp1, tmp2, tmp3, lit_rev_vars)
```

### Load time 1 data
```{r}
test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/t1_data/variables_exhaustive.csv')

@@

```{r}
test_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/t1_data/variables_exhaustive.csv')

@@

### Load time 2 data 
```{r}
retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/variables_exhaustive.csv')

@@

```{r}
hddm_refits <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/hddm_refits_exhaustive.csv')

@@

```{r}
summary(demog_rel_df)
```

@@

ggsave('Metric_Scatterplots.jpg', plot = grid.arrange(p1, p2, p3, nrow=1), device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 12, height = 4, units = "in", limitsize = FALSE, dpi = 100)
```

@@

```{r message=FALSE, warning=FALSE}
boot_df <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/bootstrap_merged.csv')

@@

ggsave('Bootstrap_Poster_Plot_t.jpg', plot = p6_t, device = "jpeg", path = "../output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE, dpi = 100)
```

@@

ggsave('Variance_Breakdown_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 24, height = 20, units = "in", dpi = 100)
rm(tmp, labels)
```

@@

```{r}
tmp%>%
  group_by(task, key) %>%
  summarise(median = median(value),
            sd = sd(value))
```

Summarizing for clearer presentation. This graph is currently using the bootstrapped reliabilities and is therefore messier than if just using the point estimates.

@@

ggsave('Variance_Breakdown_Plot_Summary.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 10, height = 5, units = "in", dpi = 100)
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            min_icc = min(icc),
            max_icc = max(icc),
            min_spearman = min(spearman),
            max_spearman = max(spearman),
            num_measures = n()/1000,
            num_trials = unique(num_all_trials))%>%
  arrange(-median_icc, -median_spearman)

@@

```{r}
tmp = tmp%>%
  mutate(task_name = gsub("_", " ", task_name),
         task_name = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", task_name, perl=TRUE))

names(tmp) = gsub("_", " ", names(tmp))
names(tmp) = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", names(tmp), perl=TRUE)

sjt.df(tmp %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/task_rel_table.doc")
```
